Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
Update manuscript.Rmd and ~$nuscript.docx

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
   ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
   ^2^Department of Biology, Memorial University of Newfoundland, Canada
   #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
  #  reference_docx: template.docx
bibliography: ../references/knitcite.bib
#csl: csl.csl
---

>>>>

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
   ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
   ^2^Department of Biology, Memorial University of Newfoundland, Canada
   #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/knitcite.bib
#csl: csl.csl
---
